A Semantic Proof of Generalised Cut Elimination for Deep Inference

### 2025-05-02 journal-version/sections/mav-semantics.tex
[ tex ] Ported paper to LMCS class, except for appendix

\begin{definition}\label[defn]{defn:pomonoid}
  A \emph{partial order monoid (pomonoid)} $(\bullet, i)$ on a poset
  $(A, \leq)$ comprises a binary operator $\bullet : A \times A \to A$
  that is monotone in both arguments and an element $i \in A$ such
  that the usual monoid laws hold. A \emph{commutative pomonoid} is a
  pomonoid where additionally $x \bullet y = y \bullet x$.
\end{definition}

\begin{definition}\label[defn]{defn:residual}
  A commutative pomonoid $(\bullet, i)$ on a poset $(A, \leq)$ is
  \emph{residuated} if there is a function
  $\rightblackspoon : A \times A \to A$ such that $x \bullet y \leq z$
  iff $x \leq y \rightblackspoon z$.
\end{definition}

@@

\begin{definition}\label[defn]{defn:star-autonomous}
  A \emph{$*$-autonomous partial order} is a structure
  $(A, \leq, \otimes, I, \lnot)$ where $(\otimes, I)$ is a pomonoid on
  $(A, \leq)$ and $\lnot : A^\op \to A$ is an anti-monotone and
  involutive operator on $A$, together satisfying
  $x \otimes y \leq \lnot z$ iff $x \leq \lnot (y \otimes z)$.  A
  $*$-autonomous partial order satisfies \emph{mix} if $\lnot I = I$.
\end{definition}

\begin{remark}
  The structure of a $*$-autonomous partial order has a number of
  immediate consequences, but we leave description of these until
  after the definition of MAV-algebra in \Cref{defn:mav-algebra}.
\end{remark}

@@

\begin{definition}\label[defn]{defn:duoidal}
  A pomonoid $(\bullet, i)$ is \emph{duoidal over} another pomonoid
  $(\lhd, j)$ on a partial order $(A, \leq)$ if the following
  inequalities hold:
  \begin{enumerate}
    \item $(w \lhd x) \bullet (y \lhd z) \leq (w \bullet y) \lhd (x \bullet z)$
    \item $j \bullet j \leq j$
    \item $i \leq i \lhd i$
    \item $i \leq j$
  \end{enumerate}
\end{definition}

\begin{remark}
  In the case when the two pomonoids share a common unit the last
  three conditions for a duoidal relationship are automatically
  satisfied. We can also ignore the existence of the units and just
  describe two binary operators as being duoidal. If $\bullet$ is a
  join, or $\lhd$ is a meet, then all the conditions for a duoidal
  relationship are automatically met.
\end{remark}

@@

\begin{definition}\label[defn]{defn:mav-algebra}
  An \emph{MAV-algebra} is a structure
  $(A, \leq, \otimes, \lhd, I, \lnot)$ with the following properties:
  \begin{enumerate}
    \item $(A, \leq, \otimes, I, \lnot)$ is $*$-autonomous and satisfies \emph{mix}.
    \item $(A, \leq, \lhd, I)$ is a pomonoid.
    \item $\lhd$ is self dual: $\lnot (x \lhd y) = (\lnot x)\lhd (\lnot y)$.
    \item $(\otimes, I)$ is duoidal over $(\lhd, I)$.
    \item $(A, \leq)$ has binary meets, which we write as $x \with y$.
  \end{enumerate}
\end{definition}

\begin{proposition}\label[prop]{prop:mav-algebra-consequences}
  Let $(A, \leq, \otimes, \lhd, I, \lnot)$ be a MAV-algebra.
  \begin{enumerate}
    \item There is another commutative pomonoid structure $(\parr, I)$ on
          $(A, \leq)$, defined as
          $x \parr y = \lnot(\lnot x \otimes \lnot y)$.
    \item $(\otimes, I)$ and $(\parr, I)$ are linearly distributive
          \cite{Cockett_1999}:
          $x \otimes (y \parr z) \leq (x \otimes y) \parr z$.
    \item $(A, \leq)$ has binary joins, given by
          $x \oplus y = \lnot (\lnot x \with \lnot y)$.
    \item $\oplus$ distributes over $\otimes$:
          $x \otimes (y \oplus z) = (x \otimes y) \oplus (x \otimes z)$.
    \item $\with$ distributes over $\parr$:
          $(x \parr z) \with (y \parr z) = (x \with y) \parr z$.
    \item $\lhd$ is duoidal over $\parr$:
          $(w \parr x)\lhd (y \parr z) \leq (w\lhd y) \parr (x\lhd z)$.
    \item $\lhd$ is duoidal over $\with$:
          $(w \with x)\lhd (y \with z) \leq (w \lhd y) \with (x\lhd z)$.
    \item $\oplus$ is duoidal over $\lhd$:
          $(w \lhd x) \oplus (y \lhd z) \leq (x \oplus y) \lhd (x \oplus z)$.
  \end{enumerate}
\end{proposition}

\begin{definition}\label[defn]{defn:mav-interpretation}
  Let $\mathit{At}$ be a set of atomic propositions. Given an
  MAV-algebra $(A, \leq, \otimes, \lhd, I, \lnot)$ and valuation
  $V : \mathit{At} \to A$, define the interpretation of MAV Formulas
  as follows:
  $\sem{\vUnit} = I$,
  $\sem{\va} = V(\va)$,
  $\sem{\vDual \va} = \lnot V(\va)$,
  $\sem{\vP\vTens\vQ} = \sem{\vP} \otimes \sem{\vQ}$,
  $\sem{\vP\vParr\vQ} = \sem{\vP} \parr \sem{\vQ}$,
  $\sem{\vP\vSeq\vQ} = \sem{\vP}\lhd\sem{\vQ}$,
  $\sem{\vP\vWith\vQ} = \sem{\vP} \with \sem{\vQ}$, and
  $\sem{\vP\vPlus\vQ} = \sem{\vP} \oplus \sem{\vQ}$.
\end{definition}

\begin{lemma}\label[lem]{lem:dual-ok}
  For all $\vP$, $\sem{\vDual{\vP}} = \lnot \sem{\vP}$.
\end{lemma}

\begin{theorem}\label[thm]{thm:soundness}
  The interpretation in \Cref{defn:mav-interpretation} is sound:
  for all structures $\vP$,
  if $\vP\vInferFrom*\vUnit$,
  then $I \leq \sem{\vP}$.
\end{theorem}

@@

\begin{remark}
  More generally, if $P \vInferFrom* Q$ in MAV, then
  $\sem{Q} \leq \sem{P}$ in an MAV-algebra. Note that the ordering is
  reversed! It will be reversed again in the definition of MAV-frame.
\end{remark}

@@

\begin{definition}\label[defn]{defn:mav-frame}
  An \emph{MAV-frame} is a structure $(F, \leq, \parr, \lhd, i, +)$
  where $(F, \leq)$ is a partial order, $(F, \leq, \parr, i)$ is a
  commutative pomonoid, $(F, \leq, \lhd, i)$ is a pomonoid, $+$ is a
  binary monotone function on $(F, \leq)$, and these data satisfy the
  following inequalities:
  \begin{enumerate}
    \item $(w \lhd x) \parr (y \lhd z) \leq (w \parr y) \lhd (x \parr z)$
    \item $(x + y) \parr z \leq (x \parr z) + (y \parr z)$
    \item $(w \lhd x) + (y \lhd z) \leq (w + y) \lhd (x + z)$
    \item $i + i \leq i$
  \end{enumerate}
\end{definition}

\begin{remark}
  An MAV-frame is essentially two duoidal relationships and a
  distributivity law.
\end{remark}

\begin{remark}
  MAV-frames have a intuitive reading as CCS-like process algebras
  (see Milner \cite{Milner89:CC} for an introduction to CCS). If we
  assume the existence of a collection of ``action'' elements
  $a \in F$ and their duals $\overline{a} \in F$, satisfying
  $a \parr \overline{a} \leq i$, then we can read the constructs of an
  MAV-frame as parallel composition, sequential composition, and
  choice. The ordering is interpreted as a reduction relation. An
  interesting avenue for future work would be to discover to what
  extent MAV can be thought of as a logic for processes in this
  process algebra.
\end{remark}

\begin{remark}\label[remark]{remark:cka}
  MAV-frames (and MAV-algebras) are also very similar to the
  definition of a \emph{Concurrent Kleene Algebra} (CKA) due to Hoare,
  M{\"o}ller, Struth and Wehrman \cite[Definition
    4.1]{Hoare_2011}. One difference is that we do not assume that $+$
  is a join, nor do we assume the existence of infinitary
  joins. Consequently, we have no analogue of the Kleene Star. Another
  difference is that the duoidal relationship is reversed in
  MAV-frames, indicating that MAV-frames capture evolution of
  processes while MAV-algebras and CKA capture properties of
  processes.
\end{remark}

\begin{proposition}\label[prop]{prop:nmav-frame}
  The \emph{normal proof MAV-frame} \NMAV is the partial order arising
  as the quotient of the preorder formed from the structures of MAV
  and $\vP\leq\vQ$ if there is a normal derivation
  $\vP\vInferFrom*\vQ$, defined as
  $(\vSS, \vInferFrom*, \vParr, \vSeq, \vUnit, \vWith)$, where $\vSS$
  is the set of all MAV structures.  The required (in)equalities
  follow directly from the definition of $\vInferFrom*$ for normal
  proofs.
\end{proposition}

\begin{remark}
  The construction of the MAV-frame \NMAV does not use the $\vTens$
  and $\vPlus$ structure of MAV directly.  This structure is recovered
  by duality from the other connectives by the constructions in the
  rest of this section. This corresponds to the fact that the
  \textsc{Co-X} rules in MAV that we wish to show admissible are the
  ones that mention the $\vTens$ and $\vPlus$ connectives, with the
  exception of \cref{rule:Switch}, which has a special role to play in
  \Cref{prop:embedding-sem} in mediating interaction.
\end{remark}

@@

\begin{definition}\label[defn]{defn:lower-set}
  Given a partial order $(A, \leq)$, the set of lower sets
  $\LowerSet{A}$ consists of subsets $F \subseteq A$ that are
  down-closed: $x \in F$ and $y \leq x$ implies $y \in F$. Lower sets
  are ordered by inclusion. Define the embedding
  $\eta : A \to \LowerSet{A}$ as $\eta(x) = \{ y \mid y \leq x \}$.
\end{definition}

\begin{proposition}\label[defn]{defn:lower-set-embed-monotone}
  For any $(A, \leq)$, the function $\eta$ is monotone, and
  $(\LowerSet{A}, \subseteq)$ has meets and joins given by
  intersection and union respectively.
  % \bob{and $\eta$ preserves any meets that exist}
\end{proposition}

\begin{proposition}\label[prop]{prop:day-construction}
  If $(\bullet, i)$ is a pomonoid on $(A, \leq)$, then there is a
  corresponding \emph{Day pomonoid} $(\Day{\bullet}, \Day{i})$ on
  $\LowerSet{A}$ defined as
  $F \Day\bullet G = \{ z \mid z \leq x \bullet y, x \in F, y \in G
    \}$ and $\Day{i} = \eta(i)$. Moreover:
  \begin{enumerate}
    \item If $(\bullet, i)$ is a commutative pomonoid, then so is
          $(\Day{\bullet}, \Day{i})$.
    \item $(\Day{\bullet}, \Day{i})$ has left and right residuals, which
          coincide when it is commutative. We will only be interested in
          residuals for commutative pomonoids, which we write as
          $F \rightblackspoon G$.
    \item The embedding preserves the monoid:
          $\eta(x \bullet y) = \eta(x) \Day\bullet \eta(y)$.
  \end{enumerate}
\end{proposition}

\begin{remark}
  \Cref{prop:day-construction} is the Day monoidal product on functor
  categories \cite{Day_1970} restricted to the case of partial orders
  and lower sets.
\end{remark}

\begin{remark}
  When $(A, \leq)$ is an MAV-frame, \Cref{prop:day-construction} gives us two pomonoids
  $(\Day{\parr}, \Day{I})$ and $(\Day{\lhd}, \Day{I})$ on
  $\LowerSet{A}$. Moreover, the next proposition states that the
  duoidal relationship between these monoids is preserved by the Day
  construction:
\end{remark}

\begin{proposition}\label[prop]{prop:lower-set-duoidal}
  If $(\bullet, i)$ is duoidal over $(\lhd, j)$ then
  $(\Day{\bullet}, \Day{i})$ is duoidal over $(\Day{\lhd}, \Day{j})$.
\end{proposition}

@@

\begin{definition}\label[defn]{defn:closed-lower-set}
  A lower set $F \in \LowerSet{A}$ is \emph{$+$-closed} if $x \in F$
  and $y \in F$ imply $x + y \in F$. $+$-closed lower sets are ordered
  by subset inclusion and form a partial order
  $(\ClosedLowerSet{A}, \subseteq)$.
\end{definition}

\begin{proposition}
  Let $U : \ClosedLowerSet{A} \to \LowerSet{A}$ be the ``forgetful''
  function that forgets the $+$-closed property. There is a monotone
  function $\alpha : \LowerSet{A} \to \ClosedLowerSet{A}$ such that
  for all $F \in \ClosedLowerSet{A}$, $\alpha(U F) = F$ and for all
  $F \in \LowerSet{A}$, $F \subseteq U (\alpha F)$.
\end{proposition}

@@

\begin{definition}
  Define the embedding $\eta^+ : A \to \ClosedLowerSet{A}$ as
  $\eta^+(x) = \alpha(\eta(x))$.
\end{definition}

\begin{remark}
  By this proposition, $U \circ \alpha$ is a closure operator on
  $\LowerSet{A}$ \cite{Davey_2002}, and the closed elements are
  those of $\ClosedLowerSet{A}$. The next proposition is standard for
  showing that meets and joins exist on the closed elements for some
  closure operator.
\end{remark}

\begin{proposition}
  $(\ClosedLowerSet{A}, \subseteq)$ has all meets and joins. In the
  binary case, meets are defined by intersection and joins are defined
  by $F \lor G = \alpha (U F \cup U G)$.
\end{proposition}

\begin{proposition}\label[prop]{prop:closed-eta-preserve-joins}
  $\eta^+(x + y) \subseteq \eta^+(x) \lor \eta^+(y)$.
\end{proposition}

\begin{remark}
  \Cref{prop:closed-eta-preserve-joins} is the reason for
  requiring $+$-closure. This property will allow us to prove the
  crucial embedding property for all structures in \Cref{sec:mav-cut-elimination}.
\end{remark}

\begin{proposition}\label[prop]{prop:closed-monoid-distrib}
  For a commutative pomonoid $(\bullet, i)$ on $(A, \leq)$ that
  distributes over $+$
  (i.e., $(x + y) \bullet z \leq (x \bullet z) + (y \bullet z)$ holds), we have that
  $F \ClosedDay{\bullet} G = \alpha(U F \Day{\bullet} U G)$ and
  $\ClosedDay{j} = \alpha(\Day{j})$ define a residuated commutative
  pomonoid on $\ClosedLowerSet{A}$. Moreover,
  $\eta^+(x \bullet y) = \eta^+(x) \ClosedDay{\bullet} \eta^+(y)$.
\end{proposition}

@@

\begin{proposition}\label[prop]{prop:closed-monoid-duoidal}
  For a pomonoid $(\lhd, j)$ on $(A, \leq)$, if this satisfies
  $(w \lhd x) + (y \lhd z) \leq (w + y) \lhd (x + z)$ then the Day
  construction
  $F \Day{\lhd} G = \{ z \mid z \leq x \lhd y, x \in F, y \in G \}$ on
  lower sets is $+$-closed when $F$ and $G$ are. We write
  $F \ClosedDay{\lhd} G$ to indicate when we mean this construction as
  an operation on $+$-closed lower sets. If $j + j \leq j$, then the
  Day unit $\Day{j} = \eta(j)$ is also closed and we write it as
  $\ClosedDay{j} \in \ClosedLowerSet{A}$. Together
  $(\ClosedDay{\lhd}, \ClosedDay{j})$ form a pomonoid on
  $(\ClosedLowerSet{A}, \subseteq)$. Moreover,
  $\eta^+(x \lhd y) \leq \eta^+(x) \ClosedDay{\lhd} \eta^+(y)$.
\end{proposition}

@@

\begin{remark}
  Generalising the situation for the unit $j$ in \Cref{prop:closed-monoid-duoidal}, $\eta(x)$ is closed for any $x$
  such that $x + x \leq x$. Note that if $+$ were a join on
  $(A, \leq)$, then this would automatically be satisfied.
\end{remark}

\begin{remark}
  We have used the same decoration $\ClosedDay{\bullet}$ and
  $\ClosedDay{\lhd}$ for two separate constructions of pomonoids on
  $+$-closed lower sets. We will be careful to distinguish which we
  mean: in our present application, a symmetric operator like
  $\bullet$ will distribute over $+$ and so $\ClosedDay{\bullet}$ will
  be constructed by \Cref{prop:closed-monoid-distrib}; and
  a non-symmetric operator like $\lhd$ will be duoidal under $+$ and
  so $\ClosedDay{\lhd}$ will be constructed by \Cref{prop:closed-monoid-duoidal}.
\end{remark}

\begin{remark}
  If we have two pomonoids on $(A, \leq)$ that share a unit, then the
  two constructions of units in \Cref{prop:closed-monoid-distrib,prop:closed-monoid-duoidal} will yield the same element of
  $\ClosedLowerSet{A}$.
\end{remark}

\begin{proposition}
  If $(\bullet, i)$ is duoidal over $(\lhd, j)$ on $(A, \leq)$, and
  $(\bullet, i)$ distributes over $+$ (as in \Cref{prop:closed-monoid-distrib}) and $+$ is duoidal over
  $(\lhd, j)$ (as in \Cref{prop:closed-monoid-duoidal}),
  then $(\ClosedDay{\bullet}, \ClosedDay{i})$ is duoidal over
  $(\ClosedDay{\lhd}, \ClosedDay{j})$ on
  $(\ClosedLowerSet{A}, \subseteq)$.
\end{proposition}

@@

\begin{remark}
  When $k = j$, the two conditions in the proposition are
  automatically satisfied. Moreover, if $k = i = j$, then not only
  does the $*$-autonomous structure satisfy \emph{mix}, but we also
  have $I =J$.
\end{remark}

>>>>

\begin{defi}\label[defn]{defn:pomonoid}
  A \emph{partial order monoid (pomonoid)} $(\bullet, i)$ on a poset
  $(A, \leq)$ comprises a binary operator $\bullet : A \times A \to A$
  that is monotone in both arguments and an element $i \in A$ such
  that the usual monoid laws hold. A \emph{commutative pomonoid} is a
  pomonoid where additionally $x \bullet y = y \bullet x$.
\end{defi}

\begin{defi}\label[defn]{defn:residual}
  A commutative pomonoid $(\bullet, i)$ on a poset $(A, \leq)$ is
  \emph{residuated} if there is a function
  $\rightblackspoon : A \times A \to A$ such that $x \bullet y \leq z$
  iff $x \leq y \rightblackspoon z$.
\end{defi}

@@

\begin{defi}\label[defn]{defn:star-autonomous}
  A \emph{$*$-autonomous partial order} is a structure
  $(A, \leq, \otimes, I, \lnot)$ where $(\otimes, I)$ is a pomonoid on
  $(A, \leq)$ and $\lnot : A^\op \to A$ is an anti-monotone and
  involutive operator on $A$, together satisfying
  $x \otimes y \leq \lnot z$ iff $x \leq \lnot (y \otimes z)$.  A
  $*$-autonomous partial order satisfies \emph{mix} if $\lnot I = I$.
\end{defi}

\begin{rem}
  The structure of a $*$-autonomous partial order has a number of
  immediate consequences, but we leave description of these until
  after the definition of MAV-algebra in \Cref{defn:mav-algebra}.
\end{rem}

@@

\begin{defi}\label[defn]{defn:duoidal}
  A pomonoid $(\bullet, i)$ is \emph{duoidal over} another pomonoid
  $(\lhd, j)$ on a partial order $(A, \leq)$ if the following
  inequalities hold:
  \begin{enumerate}
    \item $(w \lhd x) \bullet (y \lhd z) \leq (w \bullet y) \lhd (x \bullet z)$
    \item $j \bullet j \leq j$
    \item $i \leq i \lhd i$
    \item $i \leq j$
  \end{enumerate}
\end{defi}

\begin{rem}
  In the case when the two pomonoids share a common unit the last
  three conditions for a duoidal relationship are automatically
  satisfied. We can also ignore the existence of the units and just
  describe two binary operators as being duoidal. If $\bullet$ is a
  join, or $\lhd$ is a meet, then all the conditions for a duoidal
  relationship are automatically met.
\end{rem}

@@

\begin{defi}\label[defn]{defn:mav-algebra}
  An \emph{MAV-algebra} is a structure
  $(A, \leq, \otimes, \lhd, I, \lnot)$ with the following properties:
  \begin{enumerate}
    \item $(A, \leq, \otimes, I, \lnot)$ is $*$-autonomous and satisfies \emph{mix}.
    \item $(A, \leq, \lhd, I)$ is a pomonoid.
    \item $\lhd$ is self dual: $\lnot (x \lhd y) = (\lnot x)\lhd (\lnot y)$.
    \item $(\otimes, I)$ is duoidal over $(\lhd, I)$.
    \item $(A, \leq)$ has binary meets, which we write as $x \with y$.
  \end{enumerate}
\end{defi}

\begin{prop}\label[prop]{prop:mav-algebra-consequences}
  Let $(A, \leq, \otimes, \lhd, I, \lnot)$ be a MAV-algebra.
  \begin{enumerate}
    \item There is another commutative pomonoid structure $(\parr, I)$ on
          $(A, \leq)$, defined as
          $x \parr y = \lnot(\lnot x \otimes \lnot y)$.
    \item $(\otimes, I)$ and $(\parr, I)$ are linearly distributive
          \cite{Cockett_1999}:
          $x \otimes (y \parr z) \leq (x \otimes y) \parr z$.
    \item $(A, \leq)$ has binary joins, given by
          $x \oplus y = \lnot (\lnot x \with \lnot y)$.
    \item $\oplus$ distributes over $\otimes$:
          $x \otimes (y \oplus z) = (x \otimes y) \oplus (x \otimes z)$.
    \item $\with$ distributes over $\parr$:
          $(x \parr z) \with (y \parr z) = (x \with y) \parr z$.
    \item $\lhd$ is duoidal over $\parr$:
          $(w \parr x)\lhd (y \parr z) \leq (w\lhd y) \parr (x\lhd z)$.
    \item $\lhd$ is duoidal over $\with$:
          $(w \with x)\lhd (y \with z) \leq (w \lhd y) \with (x\lhd z)$.
    \item $\oplus$ is duoidal over $\lhd$:
          $(w \lhd x) \oplus (y \lhd z) \leq (x \oplus y) \lhd (x \oplus z)$.
  \end{enumerate}
\end{prop}

\begin{defi}\label[defn]{defn:mav-interpretation}
  Let $\mathit{At}$ be a set of atomic propositions. Given an
  MAV-algebra $(A, \leq, \otimes, \lhd, I, \lnot)$ and valuation
  $V : \mathit{At} \to A$, define the interpretation of MAV Formulas
  as follows:
  $\sem{\vUnit} = I$,
  $\sem{\va} = V(\va)$,
  $\sem{\vDual \va} = \lnot V(\va)$,
  $\sem{\vP\vTens\vQ} = \sem{\vP} \otimes \sem{\vQ}$,
  $\sem{\vP\vParr\vQ} = \sem{\vP} \parr \sem{\vQ}$,
  $\sem{\vP\vSeq\vQ} = \sem{\vP}\lhd\sem{\vQ}$,
  $\sem{\vP\vWith\vQ} = \sem{\vP} \with \sem{\vQ}$, and
  $\sem{\vP\vPlus\vQ} = \sem{\vP} \oplus \sem{\vQ}$.
\end{defi}

\begin{lem}\label[lem]{lem:dual-ok}
  For all $\vP$, $\sem{\vDual{\vP}} = \lnot \sem{\vP}$.
\end{lem}

\begin{thm}\label[thm]{thm:soundness}
  The interpretation in \Cref{defn:mav-interpretation} is sound:
  for all structures $\vP$,
  if $\vP\vInferFrom*\vUnit$,
  then $I \leq \sem{\vP}$.
\end{thm}

@@

\begin{rem}
  More generally, if $P \vInferFrom* Q$ in MAV, then
  $\sem{Q} \leq \sem{P}$ in an MAV-algebra. Note that the ordering is
  reversed! It will be reversed again in the definition of MAV-frame.
\end{rem}

@@

\begin{defi}\label[defn]{defn:mav-frame}
  An \emph{MAV-frame} is a structure $(F, \leq, \parr, \lhd, i, +)$
  where $(F, \leq)$ is a partial order, $(F, \leq, \parr, i)$ is a
  commutative pomonoid, $(F, \leq, \lhd, i)$ is a pomonoid, $+$ is a
  binary monotone function on $(F, \leq)$, and these data satisfy the
  following inequalities:
  \begin{enumerate}
    \item $(w \lhd x) \parr (y \lhd z) \leq (w \parr y) \lhd (x \parr z)$
    \item $(x + y) \parr z \leq (x \parr z) + (y \parr z)$
    \item $(w \lhd x) + (y \lhd z) \leq (w + y) \lhd (x + z)$
    \item $i + i \leq i$
  \end{enumerate}
\end{defi}

\begin{rem}
  An MAV-frame is essentially two duoidal relationships and a
  distributivity law.
\end{rem}

\begin{rem}
  MAV-frames have a intuitive reading as CCS-like process algebras
  (see Milner \cite{Milner89:CC} for an introduction to CCS). If we
  assume the existence of a collection of ``action'' elements
  $a \in F$ and their duals $\overline{a} \in F$, satisfying
  $a \parr \overline{a} \leq i$, then we can read the constructs of an
  MAV-frame as parallel composition, sequential composition, and
  choice. The ordering is interpreted as a reduction relation. An
  interesting avenue for future work would be to discover to what
  extent MAV can be thought of as a logic for processes in this
  process algebra.
\end{rem}

\begin{rem}\label[remark]{remark:cka}
  MAV-frames (and MAV-algebras) are also very similar to the
  definition of a \emph{Concurrent Kleene Algebra} (CKA) due to Hoare,
  M{\"o}ller, Struth and Wehrman \cite[Definition
    4.1]{Hoare_2011}. One difference is that we do not assume that $+$
  is a join, nor do we assume the existence of infinitary
  joins. Consequently, we have no analogue of the Kleene Star. Another
  difference is that the duoidal relationship is reversed in
  MAV-frames, indicating that MAV-frames capture evolution of
  processes while MAV-algebras and CKA capture properties of
  processes.
\end{rem}

\begin{prop}\label[prop]{prop:nmav-frame}
  The \emph{normal proof MAV-frame} \NMAV is the partial order arising
  as the quotient of the preorder formed from the structures of MAV
  and $\vP\leq\vQ$ if there is a normal derivation
  $\vP\vInferFrom*\vQ$, defined as
  $(\vSS, \vInferFrom*, \vParr, \vSeq, \vUnit, \vWith)$, where $\vSS$
  is the set of all MAV structures.  The required (in)equalities
  follow directly from the definition of $\vInferFrom*$ for normal
  proofs.
\end{prop}

\begin{rem}
  The construction of the MAV-frame \NMAV does not use the $\vTens$
  and $\vPlus$ structure of MAV directly.  This structure is recovered
  by duality from the other connectives by the constructions in the
  rest of this section. This corresponds to the fact that the
  \textsc{Co-X} rules in MAV that we wish to show admissible are the
  ones that mention the $\vTens$ and $\vPlus$ connectives, with the
  exception of \cref{rule:Switch}, which has a special role to play in
  \Cref{prop:embedding-sem} in mediating interaction.
\end{rem}

@@

\begin{defi}\label[defn]{defn:lower-set}
  Given a partial order $(A, \leq)$, the set of lower sets
  $\LowerSet{A}$ consists of subsets $F \subseteq A$ that are
  down-closed: $x \in F$ and $y \leq x$ implies $y \in F$. Lower sets
  are ordered by inclusion. Define the embedding
  $\eta : A \to \LowerSet{A}$ as $\eta(x) = \{ y \mid y \leq x \}$.
\end{defi}

\begin{prop}\label[defn]{defn:lower-set-embed-monotone}
  For any $(A, \leq)$, the function $\eta$ is monotone, and
  $(\LowerSet{A}, \subseteq)$ has meets and joins given by
  intersection and union respectively.
  % \bob{and $\eta$ preserves any meets that exist}
\end{prop}

\begin{prop}\label[prop]{prop:day-construction}
  If $(\bullet, i)$ is a pomonoid on $(A, \leq)$, then there is a
  corresponding \emph{Day pomonoid} $(\Day{\bullet}, \Day{i})$ on
  $\LowerSet{A}$ defined as
  $F \Day\bullet G = \{ z \mid z \leq x \bullet y, x \in F, y \in G
    \}$ and $\Day{i} = \eta(i)$. Moreover:
  \begin{enumerate}
    \item If $(\bullet, i)$ is a commutative pomonoid, then so is
          $(\Day{\bullet}, \Day{i})$.
    \item $(\Day{\bullet}, \Day{i})$ has left and right residuals, which
          coincide when it is commutative. We will only be interested in
          residuals for commutative pomonoids, which we write as
          $F \rightblackspoon G$.
    \item The embedding preserves the monoid:
          $\eta(x \bullet y) = \eta(x) \Day\bullet \eta(y)$.
  \end{enumerate}
\end{prop}

\begin{rem}
  \Cref{prop:day-construction} is the Day monoidal product on functor
  categories \cite{Day_1970} restricted to the case of partial orders
  and lower sets.
\end{rem}

\begin{rem}
  When $(A, \leq)$ is an MAV-frame, \Cref{prop:day-construction} gives us two pomonoids
  $(\Day{\parr}, \Day{I})$ and $(\Day{\lhd}, \Day{I})$ on
  $\LowerSet{A}$. Moreover, the next proposition states that the
  duoidal relationship between these monoids is preserved by the Day
  construction:
\end{rem}

\begin{prop}\label[prop]{prop:lower-set-duoidal}
  If $(\bullet, i)$ is duoidal over $(\lhd, j)$ then
  $(\Day{\bullet}, \Day{i})$ is duoidal over $(\Day{\lhd}, \Day{j})$.
\end{prop}

@@

\begin{defi}\label[defn]{defn:closed-lower-set}
  A lower set $F \in \LowerSet{A}$ is \emph{$+$-closed} if $x \in F$
  and $y \in F$ imply $x + y \in F$. $+$-closed lower sets are ordered
  by subset inclusion and form a partial order
  $(\ClosedLowerSet{A}, \subseteq)$.
\end{defi}

\begin{prop}
  Let $U : \ClosedLowerSet{A} \to \LowerSet{A}$ be the ``forgetful''
  function that forgets the $+$-closed property. There is a monotone
  function $\alpha : \LowerSet{A} \to \ClosedLowerSet{A}$ such that
  for all $F \in \ClosedLowerSet{A}$, $\alpha(U F) = F$ and for all
  $F \in \LowerSet{A}$, $F \subseteq U (\alpha F)$.
\end{prop}

@@

\begin{defi}
  Define the embedding $\eta^+ : A \to \ClosedLowerSet{A}$ as
  $\eta^+(x) = \alpha(\eta(x))$.
\end{defi}

\begin{rem}
  By this proposition, $U \circ \alpha$ is a closure operator on
  $\LowerSet{A}$ \cite{Davey_2002}, and the closed elements are
  those of $\ClosedLowerSet{A}$. The next proposition is standard for
  showing that meets and joins exist on the closed elements for some
  closure operator.
\end{rem}

\begin{prop}
  $(\ClosedLowerSet{A}, \subseteq)$ has all meets and joins. In the
  binary case, meets are defined by intersection and joins are defined
  by $F \lor G = \alpha (U F \cup U G)$.
\end{prop}

\begin{prop}\label[prop]{prop:closed-eta-preserve-joins}
  $\eta^+(x + y) \subseteq \eta^+(x) \lor \eta^+(y)$.
\end{prop}

\begin{rem}
  \Cref{prop:closed-eta-preserve-joins} is the reason for
  requiring $+$-closure. This property will allow us to prove the
  crucial embedding property for all structures in \Cref{sec:mav-cut-elimination}.
\end{rem}

\begin{prop}\label[prop]{prop:closed-monoid-distrib}
  For a commutative pomonoid $(\bullet, i)$ on $(A, \leq)$ that
  distributes over $+$
  (i.e., $(x + y) \bullet z \leq (x \bullet z) + (y \bullet z)$ holds), we have that
  $F \ClosedDay{\bullet} G = \alpha(U F \Day{\bullet} U G)$ and
  $\ClosedDay{j} = \alpha(\Day{j})$ define a residuated commutative
  pomonoid on $\ClosedLowerSet{A}$. Moreover,
  $\eta^+(x \bullet y) = \eta^+(x) \ClosedDay{\bullet} \eta^+(y)$.
\end{prop}

@@

\begin{prop}\label[prop]{prop:closed-monoid-duoidal}
  For a pomonoid $(\lhd, j)$ on $(A, \leq)$, if this satisfies
  $(w \lhd x) + (y \lhd z) \leq (w + y) \lhd (x + z)$ then the Day
  construction
  $F \Day{\lhd} G = \{ z \mid z \leq x \lhd y, x \in F, y \in G \}$ on
  lower sets is $+$-closed when $F$ and $G$ are. We write
  $F \ClosedDay{\lhd} G$ to indicate when we mean this construction as
  an operation on $+$-closed lower sets. If $j + j \leq j$, then the
  Day unit $\Day{j} = \eta(j)$ is also closed and we write it as
  $\ClosedDay{j} \in \ClosedLowerSet{A}$. Together
  $(\ClosedDay{\lhd}, \ClosedDay{j})$ form a pomonoid on
  $(\ClosedLowerSet{A}, \subseteq)$. Moreover,
  $\eta^+(x \lhd y) \leq \eta^+(x) \ClosedDay{\lhd} \eta^+(y)$.
\end{prop}

@@

\begin{rem}
  Generalising the situation for the unit $j$ in \Cref{prop:closed-monoid-duoidal}, $\eta(x)$ is closed for any $x$
  such that $x + x \leq x$. Note that if $+$ were a join on
  $(A, \leq)$, then this would automatically be satisfied.
\end{rem}

\begin{rem}
  We have used the same decoration $\ClosedDay{\bullet}$ and
  $\ClosedDay{\lhd}$ for two separate constructions of pomonoids on
  $+$-closed lower sets. We will be careful to distinguish which we
  mean: in our present application, a symmetric operator like
  $\bullet$ will distribute over $+$ and so $\ClosedDay{\bullet}$ will
  be constructed by \Cref{prop:closed-monoid-distrib}; and
  a non-symmetric operator like $\lhd$ will be duoidal under $+$ and
  so $\ClosedDay{\lhd}$ will be constructed by \Cref{prop:closed-monoid-duoidal}.
\end{rem}

\begin{rem}
  If we have two pomonoids on $(A, \leq)$ that share a unit, then the
  two constructions of units in \Cref{prop:closed-monoid-distrib,prop:closed-monoid-duoidal} will yield the same element of
  $\ClosedLowerSet{A}$.
\end{rem}

\begin{prop}
  If $(\bullet, i)$ is duoidal over $(\lhd, j)$ on $(A, \leq)$, and
  $(\bullet, i)$ distributes over $+$ (as in \Cref{prop:closed-monoid-distrib}) and $+$ is duoidal over
  $(\lhd, j)$ (as in \Cref{prop:closed-monoid-duoidal}),
  then $(\ClosedDay{\bullet}, \ClosedDay{i})$ is duoidal over
  $(\ClosedDay{\lhd}, \ClosedDay{j})$ on
  $(\ClosedLowerSet{A}, \subseteq)$.
\end{prop}

@@

\begin{rem}
  When $k = j$, the two conditions in the proposition are
  automatically satisfied. Moreover, if $k = i = j$, then not only
  does the $*$-autonomous structure satisfy \emph{mix}, but we also
  have $I =J$.
\end{rem}
